%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Piyush	}{Umate}{ \urlstyle{same}
 213-322-8933 | \href{mailto:pumate@usc.edu}{pumate@usc.edu}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Southern}
\subsection{California}
\descript{MS in Computer Science}
\location{Exp. Dec 2019 | Los Angeles, CA}
\sectionsep

\subsection{Pune Institute of}
\subsection{Computer Technology}
\descript{BE in Computer Engineering}
\location{May 2015 | Pune, India}
\location{ CGPA: 9.00 / 10 }
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/piyushumate}{\bf piyushumate} \\
LinkedIn://  \href{https://www.linkedin.com/in/piyush-umate}{\bf piyush-umate} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Analysis of Algorithms \\
Foundations of Artificial Intelligence \\
Foundations \& Applications of Data Mining \\
Machine Learning \\
\sectionsep

\subsection{Undergraduate}
Data Structures \\
Computer Networks \\
Compiler Design \\
Software Engineering \\
Object Oriented Modeling \& Design \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Advanced:}
C \textbullet{}   C++ \textbullet{} Python \textbullet{} MySQL \textbullet{} PHP \\ 
\location{Proficient:}
Javascript \textbullet{} Scala \textbullet{} SASS/CSS \\
\location{Familiar:}
C\# \textbullet{}  Java \textbullet{} \LaTeX\ \\ 
\sectionsep
\subsection{Tools \& Frameworks}
Spark \textbullet{} Flask \textbullet{} Linux \textbullet{} Symfony \\
Git \textbullet{} AngularJS \textbullet{} Elasticsearch \\
Zend \textbullet{} GulpJS \textbullet{} ASP.NET \\
MongoDb \textbullet{} OpenCV
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{USC Graduate School}
\descript{| Student Assistant Programmer}
\location{June 2018 - Aug 2018 | Los Angeles, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Managed, modeled and analysed student data by building scalable web applications. 
\item Developed analytics \& reports to summarize, scrutinize \& evaluate the progress of Graduate \& PHD programs. {\bf Technologies :- C\#, ASP.NET, Javascript, SSRS, SQL, Kendo UI}
\end{tightemize}
\sectionsep

\runsubsection{AITOE Labs - IIT Bombay}
\descript{| Research Intern }
\location{Sep 2017 – Nov 2017 | Bombay, India}
\begin{tightemize}
\item Built a realtime object recognition module using OpenCV 3.3 dnn module and pretrained MobileNet-SSD Caffe model under the guidance of Prof. Ganesh Ramakrishnan and Prof. Vishal Kaushal.
\item Optimized OpenCV performance on Raspberry Pi by 30\% by utilizing ARM NEON, VFPV3 and threading building blocks optimizations.
\item Implemented a benchmarking algorithm to evaluate the performance of neural network based real time object detection algorithms on embedded devices. {\bf Technologies :- C++, OpenCV, Python.}
\end{tightemize}
\sectionsep

\runsubsection{Practo}
\descript{| Software Engineer}
\location{July 2015 – June 2017 | Bangalore, India}
\begin{tightemize}
\item Created secure anonymous web crawlers \& data scrapers to retrieve medical data from over 30 websites. {\bf Technologies :- Tor, Python Scrapy, PhantomJS.}
\item Implemented data preprocessing algorithms for refining scraped data and used Elasticsearch and {\bf MySQL} for indexing large size documents for efficient searching through the data. {\bf Technologies :- Symfony, PHP, Zend.}
\item Architected \& developed an e-commerce application called 'Store' to help 1M doctors manage their Practo product subscriptions online. Integrated tracking systems to understand user behavior and shipped a suite of support tools to reduce customer issue resolution TAT from 3 days to 5 minutes. {\bf Technologies :- Flask, AngularJS.}
\item Internationalized and localized Practo search platform as well as scaled it to 5 countries where its helping 25M patients find over 1M doctors. {\bf Technologies :- Flask, Symfony.}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}
\runsubsection{Collaborative Social Network engine for Recommendation \& Analytics}
\descript{}
Developed an application that collates users posts from Facebook, Twitter, Google+, LinkedIn \& Github, classifies posts into a set of predefined categories \& provides users with relevant collaborative recommendations using natural language processing \& machine learning. {\bf Technologies :- Python, Flask, Javascript, MongoDb.}
\sectionsep

\runsubsection{Recommendation System}
\descript{}
Movie recommendation system using collaborative filtering on MovieLens dataset. {\bf Technologies :- Python, Scala, Spark.}
\sectionsep

\runsubsection{Othello AI bot}
\descript{}
Developed an adversarial game search module in {\bf Python} for Othello to determine the next best move for the player using Alpha-Beta pruning. 
\sectionsep
\end{minipage} 
\end{document}  \documentclass[]{article}